\documentclass[11pt]{article}

\usepackage{mathpazo}
\usepackage[pdftex,
            pdfauthor={The TLS 15 Organizing Committee},
            pdftitle={TLS 15: Call For Papers},
            % pdfsubject={},
            % pdfkeywords={},
            pdfproducer={LaTeX with mathpazo and hyperref},
            pdfcreator={pdflatex}]{hyperref}

\begin{document}

\clearpage\thispagestyle{empty}

\section*{TLS 15}

The 15$^{\rm th}$ meeting of the \href{http://tls.ling.utexas.edu}{Texas Linguistic Society} will take place \textbf{October 24--26, 2014} at the \href{https://www.utexas.edu/cola/depts/linguistics/}{University of Texas at Austin}. Our keynote speakers include T. Florian Jaeger (University of Rochester), Philippe Schlenker (New York University), and David I. Beaver (University of Texas at Austin).

\subsection*{Call For Papers}

We invite papers from all areas of linguistics, but especially encourage submissions relevant to our special session, entitled ``\textbf{Experimental Advantages}.''
This session will consider the importance of experimental evidence in theories of syntax and semantics, and focus on research that highlights the unique advantages of the experimental environment, as opposed to other sources of data.

\bigskip\noindent
\textbf{Requirements:}

\begin{itemize}
  \setlength{\itemsep}{2pt}
  \setlength{\parskip}{2pt}
  \item Maximum 500 words for the text of the abstract. The abstract title, text, examples, figures, and references must not exceed two pages.
  \item All abstracts will be reviewed anonymously. The abstract should not include the author’s name, affiliation, or other identifying information; be careful that your name and email are not automatically embedded by your word processor.
  \item To submit your abstract, send it in PDF format to \href{mailto:tls.conference@gmail.com}{tls.conference@gmail.com}. Include the paper title and names of all authors and their affiliations in the body of the email.
\end{itemize}

\textbf{Deadline: May 31, 2014}

\bigskip\noindent
For submissions received before the original deadline (May 15, 2014), notifications of acceptance or rejection will be sent out by July 1, 2014. Otherwise, for submissions received before the extended deadline, notifications will be sent by July 15, 2014.

\medskip\noindent
Presentations will be 20 minutes in length, with 10 minutes for questions.

\medskip\noindent
This Call for Papers can also be found at the conference website:

\medskip
\url{http://tls.ling.utexas.edu/2014tls/}

\medskip
\noindent
\textbf{Addendum 1:}
  Maximum of two abstracts per individual; maximum of one solo abstract per individual.
  (April 24, 2014)

\noindent
\textbf{Addendum 2:}
  Deadline extended to May 31, 2014.
  (May 15, 2014)

\end{document}
