\documentclass[11pt]{article}

\usepackage{mathpazo}
\usepackage[normalem]{ulem}
\usepackage[pdftex,
            pdfauthor={The TLS 16 Organizing Committee},
            pdftitle={TLS 16: Call For Papers},
            % pdfsubject={},
            % pdfkeywords={},
            pdfproducer={LaTeX with mathpazo and hyperref},
            pdfcreator={pdflatex}]{hyperref}

\begin{document}

\clearpage\thispagestyle{empty}

\section*{TLS 16}

The 16$^{\rm th}$ meeting of the \href{http://tls.ling.utexas.edu}{Texas Linguistic Society} will take place \textbf{February 19--20, 2016} at the \href{https://www.utexas.edu/cola/depts/linguistics/}{University of Texas at Austin}. Our keynote speakers include Lisa Matthewson (The University of British Columbia), J{\"u}rgen Bohnemeyer (University at Buffalo), and Hans Kamp (University of Stuttgart; University of Texas at Austin).

\subsection*{Call For Papers}

We invite papers from all areas of linguistics, but especially encourage submissions relevant to our special session, entitled ``\textbf{Lexical Aspect and Temporality}.'' There is a great deal of typological diversity with respect to how languages encode temporality and aspectual information, and we are particularly interested in papers that focus on these topics from a wide variety of approaches.

\bigskip\noindent
\textbf{Requirements:}

\begin{itemize}
  \setlength{\itemsep}{2pt}
  \setlength{\parskip}{2pt}
  \item Maximum 500 words for the text of the abstract. The abstract title, text, examples, figures, and references must not exceed two pages.
  \item All abstracts will be reviewed anonymously. The abstract should not include the author’s name, affiliation, or other identifying information; be careful that your name and email are not automatically embedded by your word processor.
  \item To submit your abstract, send it in PDF format to \href{mailto:tls.conference@gmail.com}{tls.conference@gmail.com}. Include the paper title and names of all authors and their affiliations in the body of the email.
\end{itemize}

\textbf{Deadline: \sout{November 1, 2015}}

\textbf{Extended Deadline: November 13, 2015}

\bigskip\noindent
Notifications of acceptance or rejection will be sent out by December 15, 2015.

\medskip\noindent
Presentations will be 20 minutes in length, with 10 minutes for questions.

\medskip\noindent
Maximum of two abstracts per individual; maximum of one solo abstract per individual.

\medskip\noindent
This Call for Papers can also be found at the conference website:

\medskip
\url{tls.ling.utexas.edu/2016tls/}

\end{document}
